|

### 2024-04-17 docs/paper.qmd
Added refs to survey dashboard

```{=tex}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{github.com/joachim-gassen/osacc}  \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```
\pagebreak

@@

Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.

@@

The second stage of the survey featured a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023 . First, we asked respondents about their confidence in the reproducibility of accounting research. We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible. Next, we asked the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other). Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration. Lastly, we asked them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research. We completed the survey by asking a few demographic questions that are primarily presented in Table 2. For a complete overview of the survey questions included in our study, please see Appendix A.

@@

>>>>

```{=tex}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{github.com/joachim-gassen/osacc}  \newline
\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc/} \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```
\pagebreak

@@

Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.

@@

The second stage of the survey featured a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023 . First, we asked respondents about their confidence in the reproducibility of accounting research. We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible. Next, we asked the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other). Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration. Lastly, we asked them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research. We completed the survey by asking a few demographic questions that are primarily presented in Table 2. For a complete overview of the survey questions included in our study, please see Appendix A. Besides the findings that follow, all answers to these questions can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}.

@@

To explore our survey data in more depth, we encourage the use of our [online survey dashboard](https://jgassen.shinyapps.io/osacc/). Using this dashboard, you can explore the response to all survey questions, partitioning it by respondents' demographics.
